\chapter{Tracker}

We considerate tracker as an algorithm used to detect a position of the object in
an image. We will present few tested trackers and their results in this task.
Firstly we provide a short description of simple straightforward tracker and
then we will describe more complicated trackers.

We use a word tracker generally for an algorithm able to detect object. Some
trackers but do not take an advantage of past images and information gained
from them. They simply detect an object in the each image. On the other hand
many good trackers using also information from previous images exist. For this
task some trackers from both categories.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section {Detection based algorithms}

\subsection{Simple Background Tracker}

This tracker takes a photo of the background at the beginning and calls it
\emph{pattern}. In order to detect an object in \emph{image} is taken a
comparison of the \emph{image} and \emph{pattern}. A Comparison is done by
taking a sum of an absolute difference for each colour (Red, Green, Blue) in
the images. 

As result, we get a map, where higher values mean bigger difference between the
colors of the \emph{pattern} and \emph{image} at given point. We will assume it
is caused by an object in front of the camera at given point.  As the next step
we will binarize the map with a given \emph{treshold}. At this point we will
find a countour with biggest area using OpenCV library. Centerpoint of the
rectangle of this contour will be estimated position of our object in the
image..

\todo[inline]{Pomôže práve popísaný postup zapísať v niekoľkých riadkoch pseudokódu? Bolo
by to prehľadnejšie (na jedno pozretie jasné, bez čítania odstavca, ak čitateľ
vie, čo očakávať)}

\todo[inline]{Fotka vzoru (farebne), fotka s objektom, absolute\_diff, výsledok po rôznych tresholdoch}

\todo[inline]{Nájdenie contúr na obrázku, zobrazenie najväčšej, bod ako stred}

Advantages
\begin{itemize}
\item Quite straight-forward implementation
\item Ability to recognise variate object without having specific color or pattern.
\end{itemize}

Disadvantages
\begin{itemize}
\item Cannot recover from even small movement of the camera.
\item Moving object with a hand will cause recognizing the hand also as an object and will result wrongly estimated center of the moving object. Same problems cause shadows.
\end{itemize}

\subsection{Adaptive Background Tracker}

In order to make our background tracker robust to small movement of camera we
are going to update our \emph{pattern}. This could be simply done by defining \emph{pattern}
as the mean of last \emph{n} images.

Advantages
\begin{itemize}
\item Robust against movements of the camera
\end{itemize}

Disadvantages
\begin{itemize}
\item If the object is not moving it will disappear as becoming a part of the
background. After moving it will recover properly.
\end{itemize}

\subsection{HSV tracker}

This tracker is based on color tracking. Given an input object we find the
color with the largest area inside the object (range of color tones is used).
On position request we return a center of the largest area with given color
range.

\todo[inline]{Obrazok kde je maska a potom bod}

Advantages
- 

Disadvatages
- able to track only one color objects

\subsection {Pattern matching}

Pattern (or template) matching is based on sliding over the input image and comparing the template with the patch of the input image. TODO This algorithm is slow on big images. There for we preprocess the image beforehand by resizing it. At the other hand it may cause more false detection due to lower quality.

For patch and template comparison many different metrics may be used. We used TODO, since it perfomed best on given examples.

Metric could be written as:
$$R(x, y) = ....$$
where $x'$ and $y'$ denotes points from the neighbourhood of the $x, y$. $T$ denotes our pattern and $I$ denotes a patch from the input image. 

Advantages
- in case of different background pattern and object low change of false positives

Disadvantages
- not persistable against appearance chagnges
- computabily expensive

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tracking algorithms}

Using an advantage of information from previous frames could create not only
more stable but also faster trackers. Tracking preserves identity, which means
that also in the case multiple moving objects it remains tracking the original
one.

Sample information we can obtain from tracking information:
- velocity - from previous images we can estimate speed and the direction of
  the movement. This can reduce searching area to smaller one and increasing so
  the speed of the algorithm.
- appearance - object may rotate and change its shape or color. Tracker able to
  learn can be persistable against such changes

Algorithm using these information can cope with occlusion - what usually
detection algorithms are not able.

In the next sections we will present few trackers implemented in the OpenCV. We
will shortly describe their principle and state their advatages and
disadvantages. At the end of the chapter comparison table will be provided.

\subsection{BOOSTING tracker}
Boosting tracker is based on online AdaBoost. It consider bounding box as positive sample and patches of background as negative ones. Given a new image, classifier is run on every pixel in the neighbourhood of the previous location and the score of the classifier is recorded. The location with highest score is choosed as a new location. 

Advantages
- foundation of more successful trackers 

Disadvantages
- another trackers evolved from this idea and now perform better

H Grabner, M Grabner, and H Bischof, Real-time tracking via on-line boosting, In Proc. BMVC, volume 1, pages 47– 56, 2006
http://www.bmva.org/bmvc/2006/papers/033.pdf

\todo[inline]{Pridat do literatury https://www.learnopencv.com/object-tracking-using-opencv-cpp-python/}

\subsection{MIL tracker}



\subsection{KCF tracker}



\subsection{TLD tracker}



\subsection{MEDIANFLOW tracker}





Note: GOTURN tracker is also implemented in OpenCV, unfortunately at the time
of the writing thesis it contains bug causing it unusable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comparison of trackers}

\subsubsection{Experiment with simplyfied environment}

Given a video sequence XYZ second long we studied an accuracy of trackers. The background is one colored and moving object is a red circle.

\todo[inline]{ Robot sledujúci čiaru do štvorca s červeným kruhom z vrchu (kamery sa dívajú zvrchu). Porovnanie bude uvedené ako čiary, ktoré sú nakreslené pomocou zachytených bodov.}

\subsubsection{Experiment in complex environment}

Background consistsed of many colors and patterns. Moving object has a pattern and is partially colored as the background.

\todo[inline]{ Vyskytli sa veci, ako, že stratil polohu? V akom percente? Mám ako rozumne vyjadriť presnosť tých súradníc lepšie než od oka?}
