\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}

This thesis proposed a system for visual object localization in the 3D space.

The primary goal of this thesis was to provide a step by step guide for the task
of the localization of an object in 3D. We achieved the goal by describing
the whole problem and solving it step by step.

\bigskip

The thesis started with an overview of the related works in the are, continued
with calibration process, explaining the essential elements of the calibration.
We presented a short introduction to calibration routines used by OpenCV, and
we also described the results obtained by this process.

We implemented detection-based trackers such as \simback{}, \hsv{} and \patt{}.
We investigated available trackers in the open-source libraries. These trackers
from the OpenCV and Dlib are sequence-based. We proposed several statistics for
comparison of the trackers. We tested all trackers on several setups, measuring
their speed and accuracy. We also explored their abilities to track multiple
objects and to recover from occlusion. We presented the results in
tables and provided images for better understanding of concepts.

Based on the results, for environment with only one moving object is \simback{}
tracker most suitable. If the object has onecolored area, of the color which is
not present in the background, then the \hsv{} tracker is the best option. Both
these trackers are accurate and fast. These trackers also recover from
occlusion in contrary to the most of the others. On the other hand, if the
environment does not satisfy conditions for using \simback{} or \hsv{} tracker,
it is possible to use \medflow{}, \corr{} or \tld{} tracker. These trackers
performed well. If none of the trackers performed good enough, the last step is
to try the rest of the trackers (\mil{}, \boost{}, \mosse{} or \patt{}).

\todo[inline]{Zhoduju sa tieto vysledky s tymi v trackeri}

As the next step, we explained how projection matrices are computed. We
explained their importance in the projection of a point from 3D space to a 2D
view of each camera. The chapter also contains a description of simple
triangulation method. This method shows how to obtain a position of the
object in 3D space if the projection matrices and the positions in the images
are available.

When all previous steps were covered, we tested the proposed system in several
environments and settings. We studied the accuracy of the system by static
experiments, and by computing the estimated distances between the points and
comparing them to real values. In the end, we also provided experiments focusing
on overall experience when using the application.

The results shows that the precision over specific axes depends on the
alignment of the cameras. Parallel alignment outperformed non-parallel in the
accuracy horizontal lines (i.e. parallel to the X-axis). On the other hand,
non-parallel alignment outperformed parallel in most of the situation, when the
lines were not parallel to X-axis. The measured error for the distances was
usually under 10\%. We noticed and also explored, that the accuracy is lower,
when the points are further away from the camera. Also the points in the edge
of camera view tend to have worse accuracy.

\todo[inline]{Hrozne velakrat parallel}
\todo[inline]{staci taketo zhrnutie ci este nieco?}

\bigskip

We consider also our technical goals as fulfilled. The application can
calibrate automatically using a chessboard pattern, track one or more objects
with a chosen tracker, display the results of the localization live.
Furthermore, it can work with the recordings instead of the live camera views.
The data from calibration and localization are automatically saved. Also
adding a new tracker is possible.

\bigskip

Several areas can be explored in further work. While testing the application,
we noticed a noise in some specific axis. Additional work could explore the
cause of the noise and possible methods to eliminate it. We also noticed, that
the precision for the objects further away from the cameras is lower compared to
the precision of the closer ones. The question remains, which parameters of our
setup influence this precision and how much. A suitable extension of this
project would be the use of more cameras and explore if this setup improves the
precision.


\bigskip
As a conclusion, we consider the application usable in practice. The results
are perfectly usable for many purposes, although not fully reliable up to
millimeters. The systems provides an easy access to a trajectory of the object.
The project is suitable for all situation, where the trajectory log is needed
with only limited precision.
